Music Versus No Music Effectiveness On Cognitive Response Time and Typing Efficiency

### 2024-03-25 paper/paper.tex
swap to correct template

\documentclass[sigconf]{acmart}
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}} %chktex 1

@@

@@

\author{Jonquill Howlett}
\affiliation{%
  \institution{Colorado State University}
  \city{Berthoud}
  \state{Colorado}
  \country{USA}
  \postcode{80513-0650} %chktex 8
}
\email{jonquill.howlett@colostate.edu}

\author{Lianna Hoag}
\affiliation{%
  \institution{Colorado State University}
  \city{Fort Collins}
  \state{Colorado}
  \country{USA}
  \postcode{80525-0650} %chktex 8 %the rest of the zip will need to be corrected
}
\email{jonquill.howlett@colostate.edu} %update email

\author{Shea Spalding}
\affiliation{%
  \institution{Colorado State University}
  \city{Fort Collins}
  \state{Colorado}
  \country{USA}
  \postcode{80525-0650} %chktex 8 %the rest of the zip will need to be corrected
}
\email{jonquill.howlett@colostate.edu} %update email

\renewcommand{\shortauthors}{J. Howlett} %I don't know how to format this for three authors

\begin{abstract}
abstract
\end{abstract}

@@

This is a placeholder for a citation cos otherwise the compiler throws errors \cite{AudioDistractionsAshley}.

>>>>

\documentclass[manuscript, screen, review]{acmart} %removing review removes the numbers on left side
% documentclass was [sigconf]{acmart} changed to match with the given overleaf link

\AtBeginDocument{%
  \providecommand\BibTeX{{%  
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}} %chktex 1

@@

\setcopyright{acmcopyright}
\copyrightyear{2024}
\acmYear{2024}
\acmDOI{XXXXXXX.XXXXXXX}

@@

\author{Jonquill Howlett}
\email{jonquill.howlett@colostate.edu}
\affiliation{%
  \institution{Colorado State University}
  \city{Berthoud}
  \state{Colorado}
  \country{USA}
  \postcode{80513-0650} %chktex 8
}

\author{Lianna Hoag}
\email{jonquill.howlett@colostate.edu} %update email 
\affiliation{%
  \institution{Colorado State University}
  \city{Fort Collins}
  \state{Colorado}
  \country{USA}
  \postcode{80525-0650} %chktex 8 %the rest of the zip will need to be corrected
}

\author{Shea Spalding}
\email{jonquill.howlett@colostate.edu} %update email 
\affiliation{%
  \institution{Colorado State University}
  \city{Fort Collins}
  \state{Colorado}
  \country{USA}
  \postcode{80525-0650} %chktex 8 %the rest of the zip will need to be corrected
}

\renewcommand{\shortauthors}{Howlett, Hoag, Spalding} %I don't know how to format this for three authors 
% the template does not show any shortauthors

\begin{abstract}
The abstract does not get added until after the project is finished or nearly finished.
\end{abstract}

@@

This is a placeholder for a citation cos otherwise the compiler throws errors~\cite{AudioDistractionsAshley}.
